Remote Collection of Respiratory Samples

### 2025-07-16 Jordana Hoppe/Home Collection/manuscript.qmd
added additional survey exclusion

```{r libraries}
#| include: false
library(tidyverse)
library(lubridate)
library(gtsummary)
library(irr)
library(eulerr)
library(kableExtra)
library(caret)
library(ggstats)
library(RColorBrewer)
library(patchwork)
library(ggpubr)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning, include=FALSE}
# Use REDCap import
source(paste0(github_dir, "/CF/Jordana Hoppe/Home Collection/home_collection_data.r"))
source(paste0(github_dir, "/CF/Jordana Hoppe/Home Collection/home_collection_surveys.r"))
# Exclude missing subjects
data_exclude <- c("009-07", "009-17", "009-25", "009-37")
survey_exclude <- c(15, 27, 30, 34, 47)
data <- data %>% filter(!subject_id %in% data_exclude)
survey_data <- survey_data %>% filter(!participant_id %in% survey_exclude)
# Fix missing labels
labels <- label(data)[which(label(data) != "")]
labels[paste0(names(labels), ".factor")] <- as.character(labels)
survey_labels <- label(survey_data)[which(label(survey_data) != "")]
survey_labels[paste0(names(survey_labels), ".factor")] <- as.character(survey_labels)
labels <- c(labels, survey_labels)
# Combine race columns
races <- c(
  "American Indian or Alaska Native", "Asian", "Black or African-American",
  "Native Hawaiian or Other Pacific Islander", "White", "More than one race",
  "Unknown or not reported"
)
data$race <- apply(data, 1, function(r) {
  w <- which(r[paste0("race___", 1:7)] == 1)
  paste0(races[w], collapse = "/")
})
# Age
data$age <- round(as.numeric(ymd(data$clinic_date) - ymd(data$pt_dob)) / 365.25, 1)
# Find tests with no growth
data$clinic_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("clinic_cx_results___\\d$", names(r))]), na.rm = T)
})
data$clinic_cx_no_growth.factor <- factor(data$clinic_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
data$res_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("res_cx_results___\\d$", names(r))]), na.rm = T)
})
data$res_cx_no_growth.factor <- factor(data$res_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
data$home_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("home_cx_results___\\d$", names(r))]), na.rm = T)
})
data$home_cx_no_growth.factor <- factor(data$home_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
# Additional labels for tables
labels["race"] <- "Race"
labels["age"] <- "Age at Clinic Visit"
labels <- as.list(labels)
# Genotype format
data$Genotype <- paste0(
  data$mutation1.factor == "F508del", "/", data$mutation2.factor == "F508del"
)
data$Genotype <- factor(data$Genotype,
  levels = c("TRUE/TRUE", "TRUE/FALSE", "FALSE/FALSE"),
  labels = c("F508del/F508del", "F508del/Other", "Other/Other")
)
```

>>>>

```{r libraries}
#| include: false
library(tidyverse)
library(lubridate)
library(gtsummary)
library(irr)
library(eulerr)
library(kableExtra)
library(caret)
library(ggstats)
library(RColorBrewer)
library(patchwork)
library(ggpubr)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Documents/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning, include=FALSE}
# Use REDCap import
source(paste0(github_dir, "/CF/Jordana Hoppe/Home Collection/home_collection_data.r"))
source(paste0(github_dir, "/CF/Jordana Hoppe/Home Collection/home_collection_surveys.r"))
# Exclude missing subjects
data_exclude <- c("009-07", "009-17", "009-25", "009-37")
survey_exclude <- c(6, 15, 27, 30, 34, 47)
data <- data %>% filter(!subject_id %in% data_exclude)
survey_data <- survey_data %>% filter(!participant_id %in% survey_exclude)
# Fix missing labels
labels <- label(data)[which(label(data) != "")]
labels[paste0(names(labels), ".factor")] <- as.character(labels)
survey_labels <- label(survey_data)[which(label(survey_data) != "")]
survey_labels[paste0(names(survey_labels), ".factor")] <- as.character(survey_labels)
labels <- c(labels, survey_labels)
# Combine race columns
races <- c(
  "American Indian or Alaska Native", "Asian", "Black or African-American",
  "Native Hawaiian or Other Pacific Islander", "White", "More than one race",
  "Unknown or not reported"
)
data$race <- apply(data, 1, function(r) {
  w <- which(r[paste0("race___", 1:7)] == 1)
  paste0(races[w], collapse = "/")
})
# Age
data$age <- round(as.numeric(ymd(data$clinic_date) - ymd(data$pt_dob)) / 365.25, 1)
# Find tests with no growth
data$clinic_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("clinic_cx_results___\\d$", names(r))]), na.rm = T)
})
data$clinic_cx_no_growth.factor <- factor(data$clinic_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
data$res_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("res_cx_results___\\d$", names(r))]), na.rm = T)
})
data$res_cx_no_growth.factor <- factor(data$res_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
data$home_cx_no_growth.factor <- apply(data, 1, function(r) {
  sum(as.numeric(r[grep("home_cx_results___\\d$", names(r))]), na.rm = T)
})
data$home_cx_no_growth.factor <- factor(data$home_cx_no_growth.factor,
  levels = 0:2,
  labels = c("No Growth", "Some Growth", "Some Growth")
)
# Additional labels for tables
labels["race"] <- "Race"
labels["age"] <- "Age at Clinic Visit"
labels <- as.list(labels)
# Genotype format
data$Genotype <- paste0(
  data$mutation1.factor == "F508del", "/", data$mutation2.factor == "F508del"
)
data$Genotype <- factor(data$Genotype,
  levels = c("TRUE/TRUE", "TRUE/FALSE", "FALSE/FALSE"),
  labels = c("F508del/F508del", "F508del/Other", "Other/Other")
)
```
